%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Computer Vision Researcher} % Job title
{Everest Innovation Technology Limited} % Organization
{Hong Kong} % Location
{Jun. 2019 - Aug. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Participated in developing Altizure app on iOS platform.}
\item {Implemented adaptive marching cube algorithm in mobile platform.}
\item {Built a real-time RGBD 3D reconstruction system in iOS system.}
\item {Added texture to 3D models with source RGB images.}
\item {Integrated the 3D model into AR using ARKit.}
\end{cvitems}
}



\cventry
{Software Engineering in HUAWEI Internship Programme} % Job title
{Huawei Technologies Co., Ltd.} % Organization
{Shenzhen, China} % Location
{Jun. 2017 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Participated in Convoluted Billing System(CBS) development.}
\item {Wrote python scripts to execute database instructions on MySQL and Oracle databases.}
\item {Wrote a program for communicating with MySQL database in C++ using MySQL C++ API.}
\item {Added some test cases for automatic test system.}
\item {Wrote a bash script for installing test system automatically.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Reconsruction with DJI Drone} % Job title
{Undergraduate Research, Computer Vision Lab  (Prof. Long QUAN)} % Organization
{Hong Kong} % Location
{Aug. 2017 - Aug. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Adapted DJI open source SDK for our own iOS app.}
\item {Extracted single image from DJI video stream.}
\item {Added some callback blocks to adjust images using CIContext from iOS CoreImage framework.}
\item {Used some feature detection algorithm on the image to achieve real time detection.}
\item {Learnt ffmpeg framework to encode and decode video stream.}
\item {Designed an image browser and customized camera app.}
\item {Extracted feature points from iOS ARKit to use in a SLAM system.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Researcher} % Job title
{Undergraduate Research Opportunity Programme} % Organization
{Hong Kong} % Location
{Mar. 2016 - May. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Propounded a prototype of LoT on Arduino board.}
\end{cvitems} 
}

%------------------------------------------------



%------------------------------------------------
%------------------------------------------------

\end{cventries}